---
title: "Does step count improve feelings of activiness?"
author: "Chen Yihua (Francesca)"
date: '2022-06-15'
output: html_document
---

# Load library package
```{r}
library(tidyverse)
library(skimr)
library(ggplot2)
library(ggcorrplot)
library(gmodels)
```


# Import data
```{r}
ft = read.csv('fitness_trends.csv',sep = ',')
```


#Prepare data
```{r}
ft$mood = as.factor(ft$mood)
ft$bool_of_active = as.factor(ft$bool_of_active)
```


# Data description
```{r}
summary(ft)
```


#Assumption of t.test
y is a numeric variable:step_count
x is a categorical variable with two groups:bool_of_active
```{r}
t.test(ft$step_count~ ft$bool_of_active)
```


# Check the normality assumption of y(step_count)

#by histogram
```{r}
hist(ft$step_count, col = "indianred1" )
```

#by normality test
```{r}
shapiro.test(ft$step_count)
```

It seems that step count does not follow normal distribution.
So we can’t use t-test in this case.
Instead, We should use The Wilcoxon-Mann-Whitney test.


# Hypothesis Testing
#The Wilcoxon-Mann-Whitney test
```{r}
wilcox.test(ft$step_count~ ft$bool_of_active)

```
P>0.05, there is no significant difference.
The step count do not improve the feelings of active.


# The relationships between factors
#corrplot in all variables
```{r}
model.matrix(~0+., data=ft[,-1]) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag = F, type="lower", lab=TRUE, lab_size=2)
```

# Main Findinggs
#The step count do not improve the feelings of active.
#Potential Reasons:
#The data is recorded only from one person instead of large population.
#Many reasons can affect the activeness, such as environment, learning barrier, and  bad performance on exam.. etc.


# Other Findings
#linear and scatter plot between step_count and calories_burned
```{r}
ggplot(ft, aes(x=step_count, y=calories_burned)) + 
  geom_point()+
  geom_smooth()
```

#Violin figure of mood and step_count
```{r}
ggplot(ft, aes(x=mood, y=step_count, fill=mood)) +
  geom_violin(trim=FALSE)+
  geom_boxplot(width=0.1) + theme_minimal()
```



  
  
  